\documentclass[a4paper, 11pt]{article}
\usepackage[margin=0.1\textwidth]{geometry}
\usepackage{url}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{mdwlist}
\usepackage{setspace}
\usepackage{enumitem}

% Boilerplate
\title{Jason Bens - Resume}
\author{Jason Bens}
\date{May 20, 2014}

% Remove indents - They look silly for this
\setlength{\parindent}{0pt}

% Remove section numbers - Meaningless without ToC
\setcounter{secnumdepth}{0}

% Reduce space between lines to increase information density
\setstretch{0.8}

% Remove page number - Handled explicitly
\pagestyle{fancy}
\fancyhf{}
% Footer  
\lfoot{\firstname~\lastname}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt} % Remove top hrule, too
\renewcommand{\footrulewidth}{1pt} % Remove top hrule, too


% Personal Data
\newcommand {\firstname} {Jason}
\newcommand {\lastname} {Bens}
\newcommand {\address} {
  \mbox{1204 Yates Street}\\
  \mbox{Victoria, BC}
  \mbox{V8V 4V1}
}
\newcommand {\phone} {\mbox{1-403-845-9125}}
\newcommand {\email} {\url{Jason.L.Bens@gmail.com}}
\newcommand {\linkedin} {\url{linkedin.com/in/jasonbens}}
\newcommand {\github} {\url{github.com/JasonBens}}

\begin{document}

% Header containing personal details
% Multiple columns for header
\begin{minipage}[t]{0.7\textwidth}
  \begin{center}
    {\Huge \firstname~\lastname}
  \end{center}
\end{minipage}\hfill
\begin{minipage}{0.3\textwidth}
  \begin{flushright}
    \phone \\
    \email \\
    \linkedin \\
    \github \\
  \end{flushright}
\end{minipage}

% End of header containing personal details
\hrulefill

\section{\underline{Biography}}
I'm an electrical engineer interested in finding applications for deep learning in computer-science and engineering fields. I enjoy working with embedded systems and playing with microcontrollers. Eventually, I want to bridge the gap between humans, machines, and AI, and find ways to combine them to make something greater than the sum of its parts. In my off-time, I follow my interests through online courses such as those offered by Coursera or edX.

% Skill section
\section{\underline{Skill Summary}}
  \parbox{0.16\textwidth}{
    \textbf{Programming}\\
    C\\
    Python\\
    Matlab\\
    \LaTeX\\
    Git
  }\hfill
  \parbox{0.15\textwidth}{
    \textbf{Tools}\\
    Ngspice\\
    Altium\\
    NI LabView\\
    GNURadio\\
    AutoCAD
  } \hfill
  \parbox{0.25\textwidth}{
    \textbf{Competencies}\\
    Schematic Capture\\
    PCB Fabrication\\
    Embedded Systems\\
    Firmware Development\\
    Analog/Digital Design
  } \hfill
  \parbox{0.25\textwidth}{
    \bigskip
    Machine Learning\\
    Pattern Recognition\\
    Deep Learning\\
    Neural Networks\\
    Medical Image Processing
  } \hfill
% Experience section
\section{\underline{Experience}}
  \textbf{Research Intern - Department of Neuroinformatics}
  \hfill
  Kyoto, Japan \\
  \textbf{Advanced Telecommunications Research Institute International}
  \hfill
  \emph{June 2013 - August 2013}
  \begin{itemize*}
    \item Researched application of deep learning to fMRI for decoding object representations in the brain.
    \item Implemented a stacked denoising autoencoder using Theano, a Python module for symbolic optimization of multi-dimensional math.
    \item Applied denoising autoencoder to generic object decoding in preparation for further experiments.
  \end{itemize*}
  \textbf{Research Intern - Department of Cognitive Neuroscience}
  \hfill
  Kyoto, Japan\\
  \textbf{Advanced Telecommunications Research Institute International}
  \hfill
  \emph{July 2012 - April 2013}
  \begin{itemize*}
    \item Developed visual attention and neuroplasticity experiments using MATLAB, psychophysical stimulus generators, and EEG data capture software.
    \item Preprocessed fMRI data to allow longitudinal and cross-sectional analysis of data.
    \item Extracted patterns from fMRI, EEG, MEG, and behavioural experiment data.
    \item Built classifiers from experimental data to predict spatial attention.
  \end{itemize*}
  \textbf{Lab Supervisor}
  \hfill
  Calgary, Alberta\\
  \textbf{Southern Alberta Institute of Technology}
  \hfill
  \emph{September 2010 - May 2011}
  \begin{itemize*}
    \item Supervised Electrical Engineering Technology lab during open lab hours
    \item Helped first-year students with unfinished labwork.
  \end{itemize*}


% Education Section
\section{\underline{Education}}
  \begin{description}[leftmargin=0pt]
    \begin{samepage}
      \item[B.Eng in Electrical Engineering] \hfill University of Victoria\\
      \emph{2012 -  August 2014}
    \end{samepage}
    \begin{samepage}
    \item[Diploma in Electronics Engineering Technology] \hfill Southern Alberta Institute of Technology\\
    \emph{2009 - 2011}
    \begin{itemize*}
      \item Graduated in the Dean's List
    \end{itemize*}
    \end{samepage}
    \item[Massive Open Online Courses] \hfill
      \begin{itemize*}
        \item Web Intelligence and Big Data
        \item The Brain and Space
      \end{itemize*}
  \end{description}
  
\section{\underline{Projects}}
  \begin{itemize*}
        \item Designed a portable USB battery pack as a capstone project at the University of Victoria.
        \item Designed a 20 MHz arbitrary signal generator as a capstone project at SAIT.
        \item Implemented an unsupervised image segmentation algorithm by Deng and Clausi using Markov Random Fields.
        \item Developed a software-defined PSK31 transceiver using GNU Radio. 
        \item Planned a satellite tracking and communication ground station with UVic ECOSat team as part of the Canadian Satellite Design Competition.
  \end{itemize*}
  
\section{\underline{Extracurricular Activities}}
  \begin{description}[leftmargin=0pt]
    \item[ATR Machine Learning Club] \hfill
      \begin{itemize*}
        \item Read journal articles about recent developments in the machine learning field.
        \item Present recent journal articles to colleagues at ATR (Advanced Telecommunications Research Institute International).
      \end{itemize*}
    \item[Microprocessor Group] \hfill
      \begin{itemize*}
        \item Build Engenuics embedded microcontroller kit.
        \item Develop hardware drivers for peripherals.
      \end{itemize*}
    \item[Language Learning] \hfill
      \begin{itemize*}
        \item Received private lessons in Japanese for one year.
        \item Self-directed study in Mandarin Chinese.
      \end{itemize*}
  \end{description}
    
\section{\underline{Affiliations}}
  \begin{itemize*}
    \item ASET (Past Member)
  \end{itemize*}

\end{document}